Millions of Type Errors

### 2023-09-07 programming23/paper.tex
size figs

\begin{figure}[t]
  TODO file size distribution: table or bars %% \includegraphics{img/row-distribution.pdf}
  \caption{Size of analyzed code: number of files, number of lines , and lines in edit range}
  \label{f:analysis-size}
\end{figure}

@@

@@

%  %% TODO these need to be plots, it's too much reading for the quick takeaway
%  %% put exactly this data into bars!
%  \begin{minipage}[t]{0.5\textwidth}
%    \begin{tabular}{rr}
%      Session length & \# Sessions \\\midrule
%      1 &  450 \\
%      2 &  199 \\
%      3 &  129 \\
%      4 &  73 \\
%      5 &  60 \\
%      6-10 & 150 \\
%      11-20 & 67 \\
%      21-40 & 11 \\
%      >40 & 7
%      %% max 393
%    \end{tabular}
%  \end{minipage}\begin{minipage}[t]{0.5\textwidth}
%    \begin{tabular}{rr}
%      Time delta & \# Records \\\midrule
%      0-5ms & 284 \\
%      5-1000ms & 248 \\
%      1-2s & 153 \\
%      2-5s & 232 \\
%      5-10s & 207 \\
%      10-30s & 524 \\
%      30-60s & 392 \\
%      1-2m & 394 \\
%      2-5m & 559 \\
%      5-10m & 360 \\
%      >10-60m & 502
%    \end{tabular}
%  \end{minipage}

\begin{figure}[t]
  %% TODO stacked bars?
  %% TODO align old;curr
  \begin{tabular}{lrrrrr}
    Mode             & \# Rows & E         & Any Error & In Module & In range \\
      & & & & (old ; curr) &  (old ; curr) \\\midrule
    \mnocheck{}   &   4,471 & \code{te} &    5.77\% &  0.20\% ;  2.21\% &  0.16\% ;  0.63\% \\
                  &         & \code{fs} &   59.18\% & 32.81\% ; 49.16\% &  9.17\% ; 13.13\% \\
    \mnonstrict{} &     506 & \code{te} &   25.89\% & 12.06\% ; 18.18\% &  6.32\% ;  7.91\% \\
                  &         & \code{fs} &   62.45\% & 37.94\% ; 53.75\% & 16.60\% ; 20.75\% \\
    \mstrict{}    &      24 & \code{te} &   50.00\% & 29.17\% ; 33.33\% &     0\% ;     0\% \\
                  &         & \code{fs} &   62.50\% & 50.00\% ; 58.33\% &  4.17\% ;  8.33\% 
  \end{tabular}

@@

  {Few local adds => Few people ignoring script analysis}
  \smallskip

>>>>

FILL investigate one tower

\begin{figure}[t]
  %% \includegraphics{img/row-distribution.pdf}
  \begin{tabular}{lrrr}
           & Files  &     Lines &    Edit Range \\
    Median &  7,678 &     3,115 &           926 \\
    Mean   & 11,911 &     6,497 &         3,680 \\
    Max    & 54,884 & 1,089,963 &     1,156,036 \\
    & \includegraphics[width=0.2\columnwidth]{img/files-distribution.pdf}
    & \includegraphics[width=0.2\columnwidth]{img/lines-distribution.pdf}
    & \includegraphics[width=0.2\columnwidth]{img/editrange-distribution.pdf}

  \end{tabular}

  \caption{Size of analyzed code: number of files, number of lines , and lines in edit range}
  \label{f:codebase-size}
\end{figure}

TODO .. somewhere ... out/error-density-*
TODO ... somewhere ... te leq fs : use error-density

summary of timespan :: max 1387897376 median 845648 mean 3184317.084881936 stddev 15724745.722577972
summary of event-count :: max 6079 median 138 mean 286.5851851851852 stddev 582.5752201972966

@@

  \begin{subfigure}[t]{\columnwidth}
    \caption{TODO session size}
    \label{f:sessions-size}
  \end{subfigure}

  %% TODO out/size-dist*rktd

@@

\begin{figure}[t]
  %% TODO stacked bars?
  %% TODO align old;curr
  %% TODO sep23 remove this??!
  \begin{tabular}{lrrrrr}
    Mode             & \# Rows & E         & Any Error & In Module & In range \\
      & & & & (old ; curr) &  (old ; curr) \\\midrule
    \mnocheck{}   &   4,471 & \code{te} &    5.77\% &  0.20\% ;  2.21\% &  0.16\% ;  0.63\% \\
                  &         & \code{fs} &   59.18\% & 32.81\% ; 49.16\% &  9.17\% ; 13.13\% \\
    \mnonstrict{} &     506 & \code{te} &   25.89\% & 12.06\% ; 18.18\% &  6.32\% ;  7.91\% \\
                  &         & \code{fs} &   62.45\% & 37.94\% ; 53.75\% & 16.60\% ; 20.75\% \\
    \mstrict{}    &      24 & \code{te} &   50.00\% & 29.17\% ; 33.33\% &     0\% ;     0\% \\
                  &         & \code{fs} &   62.50\% & 50.00\% ; 58.33\% &  4.17\% ;  8.33\% 
  \end{tabular}

@@

  %% TODO import code from tmp to nsa
  {Few local adds => Few people ignoring script analysis}
  \smallskip
